### 2021-01-26 introduction.tex
minor

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}. Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}, {\color{blue}including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{arzt-pldi-2014} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}}. {\color{blue}Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes}, whose goal is to protect Android users from malicious behavior~\cite{jamrozik2016mining}.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions}

>>>>

Almost two-thirds of the world population use mobile technologies~\cite{Comscore}, and the Android Operating System has dominated the market of smartphones, tablets, and others electronic devices. Due to this growing popularity, the number of incidents related to Android malicious software (malware) has significantly increased \cite{faruki2014android,tan2015securing}. Security issues in Android software applications (``apps'' for short) have become a relevant research topic, and many techniques have been developed to identify vulnerabilities in Android apps \cite{tan2015securing}, including the use of static analysis algorithms to identify source and sink paths involving sensitive data~\cite{arzt-pldi-2014} and to reveal the misuse of cryptographic primitives~\cite{krueger:ecoop-2018,rahaman:ccs-2019}. Using a different approach, researchers have also explored the use of dynamic analysis to mine Android sandboxes, whose goal is to protect Android users from malicious behavior~\cite{jamrozik2016mining}.

@@

\todo[inline]{RB.: Later we can enumerate the paper contributions here.}
